\documentclass[12pt,a4paper]{article}
\usepackage[margin=11mm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.55em}
\linespread{1.15}\selectfont
\setlist[enumerate]{itemsep=0.36em, topsep=0.32em, parsep=0pt, leftmargin=3em}

\begin{document}
\large

\begin{center}
{\LARGE \textbf{Research Presentation A}}\\[0.45em]
{\Large Presentation Evaluation Criteria}
\end{center}

\vspace{0.2em}

\section*{1. Content and Organization}

\begin{enumerate}[label=\roman*)]
  \item Overall key points/message
  \item Organization/cohesiveness (eg. clear stages, use of connectives)
  \item Audience awareness (eg. level of difficulty/interest)
\end{enumerate}

\section*{2. Delivery (eg. speed/timing/body language)}

\begin{enumerate}[label=\roman*)]
  \item Speech speed
  \item Pausing
  \item Audibility (ie. could the speaker be heard?)
  \item Eye-contact (ie. looking at the audience or camera)
  \item Body language (including gestures, stance, and pointer use)
  \item Time management
  \item Pronunciation and vocal variety (eg. intonation, stress)
\end{enumerate}

\section*{3. Visuals (eg. PowerPoint slides)}

\begin{enumerate}[label=\roman*)]
  \item Overall key points/message
  \item Amount of text
  \item Amount of images/figures etc.
  \item Mistakes (eg. spelling)
  \item Layout/formatting
  \item Visibility (ie. images/writing/[online] presenter's face clearly visible)
  \item Technical issues (eg. slides freezing/loss of battery power)
\end{enumerate}

\end{document}
